Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
described the floating-point results
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{Lucas describe here the experimental results}

@@

We split our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the fixed-point benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (14) than the multi-staged back-end (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 58\% of the benchmarks.

>>>>

@@

We split our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the fixed-point benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (14) than the multi-staged back-end (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 58\% of the benchmarks.
%
For the majority of the floating-point benchmarks, we also observe that the abstraction-based
back-end is much faster than the basic multi-staged verification approach, but both
back-ends find the same amount of solutions (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 50\% of the time required using the multi-staged
back-end, and has a median run-time 0.6\,s, which is forty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 54\% of the benchmarks.
